Evaluating the Performance and Energy Efficiency of the COSMO-ART model system

### 2014-04-24 paper_enahpc14/Sec4:Evaluation.tex
Manuel's changes

\begin{figure}[htbf]
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-2.eps}
  \caption{Time-to-solution and energy-to-solution on Tintorrum -
    Blocking mode}
  \label{fig:3}
\end{figure}

>>>>

\begin{figure*}[htbf]
  \centering
  \includegraphics[width=0.78\textwidth]{Figs/23_24_blq1_stat1.eps}
  \caption{blabla}
  \label{fig:3}
\end{figure*}

\begin{figure*}[htbf]
  \centering
  \scalebox{0.5}{\input{Figs/24hour.pstex_t}}
  \caption{24 hours simulation trace using the MPI blocking mode on Tintorrum.}
  \label{fig:3}
\end{figure*}

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}
  \caption{1 hour simulation (11h-12h) trace using the MPI blocking mode on Tintorrum.}
  \label{fig:3}
\end{figure*}

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking mode on Tintorrum.}
  \label{fig:3}
\end{figure*}
